Response to the defense feedback

### 2021-06-18 Chapter-2/Chapter-2.tex
Updates from Overleaf

\subsubsection*{Software Patch}
Once we have identified side-channel leakages, there are two common approaches to mitigate side-channel attacks. The first approach is to adopt unified behavior code when computing the secret data. For example, a control flow leakage happens when different secret inputs lead to different paths. Software developers can mitigate the leakage by executing both branches and select the result with bit-wise operations.   However, for exiting code base, it is hard to migrate all the code into a side-channel free implementation. The second approach is to introduce randomized behaviors during the execution to obfuscate the information that an attacker can retrieve. One example is cryptographic blinding~\cite{coron1999resistance}. Developers can use a random value to blend the secret key but still generate the same encrypted data with a carefully designed algorithm.  Binding values can alter the program execution to some unpredictable states and introduce the randomization to the execution. However, the binding value can also be retrieved by an attacker through other methods, including side-channel attacks. An attacker can launch an attack to retrieve the binding value to recover the secret input.
\subsection{Hardware Countermeasures}
\subsubsection*{Resource Partitioning}
Side-channel attacks usually require attackers and victims to share some hardware resources (e.g., CPU cache, MMU). A straightforward way to defend these attacks is to partition the resources and ensure the attacker and the victim never share the same hardware resource~\cite{Page2005PartitionedCA,shi2011limiting,liu2016catalyst}. For example, in a cloud computing environment, several virtual machines (VMs) can be hosted on the same physical machine and these VMs share the same last-level cache (LLC). Researchers proposed different methods to partition the LLC such as cache coloring~\cite{shi2011limiting}, using Intel Cache Allocation Technology~\cite{liu2016catalyst}.
\subsubsection*{Randomization}
This type of defense randomizes the behaviors of hardware resources to make it harder for attackers to infer secrets based on side-channel information. For example, Random Permutation Cache ~\cite{wang2007new} uses a dynamically randomized memory to cache mapping table for each different process. Vattikonda et al.~\cite{vattikonda2011eliminating} add noises to the result of the system timer to mitigate timing-based channels.

>>>>

\subsubsection*{Software Patch}
Once we have identified side-channel leakages, there are two common approaches to mitigate side-channel attacks. The first approach is to adopt unified behavior code when computing the secret data. For example, a control flow leakage happens when different secret inputs lead to different paths. Software developers can mitigate the leakage by executing both branches and select the result with bit-wise operations~\cite{Coppens:2009:PMT:1607723.1608124}. However, for exiting code base, it is hard to migrate all the code into a side-channel free implementation. The second approach is to introduce randomized behaviors during the execution to obfuscate the information that an attacker can retrieve. One example is cryptographic blinding~\cite{coron1999resistance}. Developers can use a random value to blend the secret key but still generate the same encrypted data with a carefully designed algorithm.  Binding values can alter the program execution to some unpredictable states and introduce the randomization to the execution. However, the binding value can also be retrieved by an attacker through other methods, including side-channel attacks. An attacker can launch an attack to retrieve the binding value to recover the secret input.

\subsubsection{New Implementation}
Recent work~\cite{bernstein2012security,libsodium} also proposes to design and implement clean-slate side-channel free software from scratch.

\subsection{Hardware Countermeasures}
\subsubsection*{Resource Partitioning}
Side-channel attacks usually require attackers and victims to share some hardware resources (e.g., CPU cache, MMU). A straightforward way to defend these attacks is to partition the resources and ensure the attacker and the victim never share the same hardware resource~\cite{Page2005PartitionedCA,shi2011limiting,liu2016catalyst}. For example, in a cloud computing environment, several virtual machines (VMs) can be hosted on the same physical machine and these VMs share the same last-level cache (LLC). Researchers proposed different methods to partition the LLC such as cache coloring~\cite{shi2011limiting}, using Intel Cache Allocation Technology~\cite{liu2016catalyst}.
\subsubsection*{Randomization}
This type of defense randomizes the behaviors of hardware resources to make it harder for attackers to infer secrets based on side-channel information. For example, Random Permutation Cache ~\cite{wang2007new} uses a dynamically randomized memory to cache mapping table for each different process. Vattikonda et al.~\cite{vattikonda2011eliminating} add noises to the result of the system timer to mitigate timing-based channels.
